mir\_eval

### 2014-04-30 paper/paper.tex
Added title, authors, section headings, removed ISMIR template stuff

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}

@@

% \newcommand*{\defeq}{\mathrel{\rlap{%
%                     \raisebox{0.25ex}{$\m@th\cdot$}}%
%                     \raisebox{-0.25ex}{$\m@th\cdot$}}%
%                     =}

% Title.
% ------
\title{PAPER TEMPLATE FOR ISMIR 2014}

@@

@@

\begin{document}
%
\maketitle
%
\begin{abstract}
The abstract should be placed at the top left column and should contain about 150-200 words.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

This template includes all the information about formatting manuscripts for the ISMIR 2014.
Please follow these guidelines to give the final proceedings a uniform look.
If you have any questions, please contact the Conference Management.
This template can be downloaded from the ISMIR 2014 web site (http://ismir2014.ismir.net).

\section{Page Size}\label{sec:page_size}

The proceedings will be printed on
 \underline{portrait A4-size paper} \underline{(21.0cm x 29.7cm)}.
All material on each page should fit within a rectangle of 17.2cm x 25.2cm,
centered on the page, beginning 2.0cm
from the top of the page and ending with 2.5cm from the bottom.
The left and right margins should be 1.9cm.
The text should be in two 8.2cm columns with a 0.8cm gutter.
All text must be in a two-column format.
Text must be fully justified.

\section{Typeset Text}\label{sec:typeset_text}

\subsection{Normal or Body Text}\label{subsec:body}

Please use a 10pt (point) Times font. Sans-serif or non-proportional fonts
can be used only for special purposes, such as distinguishing source code text.

The first paragraph in each section should not be indented, but all other paragraphs should be.

\subsection{Title and Authors}

The title is 14pt Times, bold, caps, upper case, centered.
Authors' names are omitted when submitting for double-blind reviewing.
The following is for making a camera-ready version.
Authors' names are centered.
The lead author's name is to be listed first (left-most), and the co-authors' names after.
If the addresses for all authors are the same, include the address only once, centered.
If the authors have different addresses, put the addresses, evenly spaced, under each authors' name.

\subsection{First Page Copyright Notice}

Please include the copyright notice exactly as it appears here in the lower left-hand corner of the page.
It is set in 8pt Times.

\subsection{Page Numbering, Headers and Footers}

Do not include headers, footers or page numbers in your submission.
These will be added when the publications are assembled.

\section{First Level Headings}

First level headings are in Times 10pt bold,
centered with 1 line of space above the section head, and 1/2 space below it.
For a section header immediately followed by a subsection header, the space should be merged.

@@

% \subsection{Figures, Tables and Captions}
% 
% All artwork must be centered, neat, clean, and legible.
% All lines should be very dark for purposes of reproduction and art work should not be hand-drawn.
% The proceedings are not in color, and therefore all figures must make sense in black-and-white form.
% Figure and table numbers and captions always appear below the figure.
% Leave 1 line space between the figure or table and the caption.
% Each figure or table is numbered consecutively. Captions should be Times 10pt.
% Place tables/figures in text as close to the reference as possible.
% References to tables and figures should be capitalized, for example:
% see \figref{fig:example} and \tabref{tab:example}.
% Figures and tables may extend across both columns to a maximum width of 17.2cm.

% \begin{table}
%  \begin{center}
%  \begin{tabular}{|l|l|}
%   \hline
%   String value & Numeric value \\
%   \hline
%   Hello ISMIR  & 2014 \\
%   \hline
%  \end{tabular}
% \end{center}
%  \caption{Table captions should be placed below the table.}
%  \label{tab:example}
% \end{table}

%\begin{figure}
% \centerline{\framebox{
% \includegraphics[width=\columnwidth]{figure.png}}}
% \caption{Figure captions should be placed below the figure.}
% \label{fig:example}
%\end{figure}

% \begin{thebibliography}{citations}
% 
% \bibitem {Author:00}
% E. Author:
% ``The Title of the Conference Paper,''
% {\it Proceedings of the International Symposium
% on Music Information Retrieval}, pp.~000--111, 2000.
% 
% \bibitem{Someone:10}
% A. Someone, B. Someone, and C. Someone:
% ``The Title of the Journal Paper,''
% {\it Journal of New Music Research},
% Vol.~A, No.~B, pp.~111--222, 2010.
% 
% \bibitem{Someone:04} X. Someone and Y. Someone: {\it Title of the Book},
%     Editorial Acme, Porto, 2012.
% 
% \end{thebibliography}

>>>>

\documentclass{article}
\usepackage{ismir2014,amsmath,cite}
\usepackage{graphicx}
\usepackage{dsfont}
\usepackage{stmaryrd}
\usepackage{braket}
%\usepackage{authblk}

@@

% ------
\title{mir\_eval}

@@

%\author[1]{Colin Raffel}
%\author[1]{Brian McFee}
%\author[2]{Justin Salamon}
%\author[2]{Eric J. Humphrey}
%\author[2]{Oriol Nieto}
%\author[1]{Dawen Liang}
%\author[1]{Daniel P. W. Ellis}
%\affil[1]{LabROSA, Dept. of Electrical Engineering\\Columbia University, New York}
%\affil[2]{Music and Audio Research Lab\\New York University, New York}

@@

\begin{document}
%
\maketitle
%
\begin{abstract}

\end{abstract}
%
\section{Evaluating MIR Algorithms}\label{sec:introduction}

\section{Tasks included in mir\_eval}

@@

\section{Comparison to Existing Implementations}

\section{Discussion}
